ms_figures

### 2018-02-21 man/ms_figures.Rmd
add new figure

>>>>

#####
**Appendix S10.** Comparison EVI previous and post

```{r}
df <- read.csv(file=here::here("data/evi", "evi_globalmeans_drouhgt.csv"), header = TRUE, sep = ',')

ggplot(df, 
       aes(x=disturb, y=mean, colour=site)) + 
  geom_point(size=2) + 
  geom_errorbar(aes(ymin = mean - se, ymax = mean + se), width = .1) +
  geom_line(aes(group=site)) + 
  facet_wrap(~disturb_year) + 
  scale_x_discrete(labels = c("1_dr" = "Drought", "0_pre" = "Previous", "2_post" = "Posterior")) + 
  theme_bw() +
  xlab("") + ylab("EVI") + 
  theme(
    strip.background = element_rect(fill = "white"),
    strip.text = element_text(face="bold", size=12),
    axis.title.y = element_text(face="bold", size=12)
  ) +
  scale_color_manual(values=c('black', 'blue', 'gray'))
```
